article title

### 2022-07-19 article.tex
Add Greek letters for math, text

% very useful for hyperlinks
\usepackage{hyperref}

@@

@@

>>>>

% very useful for hyperlinks
\usepackage[unicode]{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

% useful for Greek letters in text mode
\usepackage[cbgreek]{textgreek}

@@

% create a list of Greek letters command
\newcommand{\listgreekname}{List of Greek Letters}
\newlistof{mygreek}{grk}{\listgreekname}
\newcommand{\mygreek}[1]{%
\addcontentsline{grk}{mygreek}{\protect\numberline{\thegreek}#1}\par}
\renewcommand{\cftgrktitlefont}{\normalfont\Large\bfseries}

@@

\newpage
\section{Greek letters}
\label{sec:greek_letters}

\subsection{Greek mathematics}
\label{sec:greek_mathematics}

alpha $\alpha$ A \\
beta $\beta$ B \\
gamma $\gamma$ $\Gamma$ \\
delta $\delta$ $\Delta$ \\
epsilon$\epsilon$ E \\
zeta $\zeta$ Z \\
eta $\eta$ H\\
theta $\theta$ $\Theta$ \\
iota $\iota$ I \\
kappa $\kappa$ K \\
lambda $\lambda$ $\Lambda$ \\
mu $\mu$ M \\
nu $\nu$ N \\
xi $\xi$ $\Xi$ \\
omicron o O \\
pi $\pi$ $\Pi$\\
rho $\rho$ P \\
sgima $\sigma$ $\Sigma$ \\
tau $\tau$ T \\
upsilon $\upsilon$ $\Upsilon$ \\
phi $\phi$ $\Phi$ \\
chi $\chi$ X \\
psi $\psi$ $\Psi$ \\
omega $\omega$ $\Omega$ \\

\subsection{Greek text}
\label{sec:greek_text}

alpha \textalpha \textAlpha \\
beta \textbeta \textBeta \\
gamma \textgamma \textGamma \\
delta \textdelta \textDelta \\
epsilon \textepsilon \textEpsilon \\
zeta \textzeta \textZeta \\
eta \texteta \textEta \\
theta \texttheta \textTheta \\
iota \textiota \textIota \\
kappa \textkappa \textKappa \\
lambda \textlambda \textLambda \\
mu \textmu \textMu \\
nu \textnu \textNu \\
xi \textxi \textXi \\
omicron o O \\
pi \textpi \textPi \\
rho \textrho \textRho \\
sigma \textsigma \textSigma \\
tau \texttau \textTau \\
upsilon \textupsilon \textUpsilon \\
phi \textphi \textPhi \\
chi \textchi \textChi \\
psi \textpsi \textPsi \\
omega \textomega \textOmega \\
